\input{src/preamble}

\begin{document}

\input{src/topsection}

\vspace{-4mm}

\spacedhrule{0.9em}{-0.4em}

\input{src/techskills}

\vspace{-5mm}

\spacedhrule{1.6em}{-0.4em}

\input{src/experience}

\spacedhrule{-0.2em}{-0.4em}

\input{src/education}

% \vspace{-0.2cm}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SELECTED PROJECTS
%----------------------------------------------------------------------------------------

\roottitle{Selected Projects} % Top level section

%%%%%%%%%%%%%%%%%% JUJU %%%%%%%%%%%%%%%%% 
\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{}
{} {
\vspace{-0.4cm}
\headedsubsection % Job title entry for the current employer
{\myhref{https://github.com/juju/juju}{Juju}}
{}
{\small\bodytext{

A large scale distributed orchestration engine for managing cloud workloads on any infrastructure (Kubernetes or otherwise) across various cloud providers (e.g., \acr{AWS}, \acr{GCE}). Juju is written in Go, and has over a million lines of code. I was a core maintainer in a team of 14 engineers. See Canonical above for details of my contribution.

}}
}

%%%%%%%%%%%%%%%%%% TERRAFORM %%%%%%%%%%%%%%%%% 
\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{}
{} {
\vspace{-0.4cm}
\headedsubsection % Job title entry for the current employer
{\myhref{https://github.com/juju/terraform-provider-juju}{Terraform Juju Provider}}
{}
{\small\bodytext{A Terraform provider that enables integration with \myhref{https://github.com/juju/juju}{Juju} while managing Terraform environments. I implemented new resources and features (e.g., \myhref{https://discourse.charmhub.io/t/manual-provisioning-on-aws-using-terraform-juju-provider/10989}{manual provisioning on \acr{AWS}}), migrated the provider from the sdk2 to the provider framework (e.g., \myhref{https://github.com/juju/terraform-provider-juju/pull/264}{sample PR}), and maintained release cadence of new versions. All in Go.}}
}

%%%%%%%%%%%%%%%%%% Pycket %%%%%%%%%%%%%%%%% 

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{}
{} {
\vspace{-0.4cm}
\headedsubsection % Job title entry for the current employer
{\myhref{http://github.com/pycket/pycket}{Pycket: A meta-tracing \textsc{JIT} compiler for self-hosting Racket}}
{}
{\small\bodytext{

PhD thesis project. Developed and maintained Pycket for over five years, designing the compiler to bootstrap the entire Racket language on a meta-tracing \acr{JIT} backend. Contributed to a new \acr{IR} (linklets, see publications) for a more portable Racket run-time. Built \myhref{https://github.com/cderici/trace-draw}{performance analysis tools} and \myhref{https://github.com/cderici/abstract-machine-interp}{formalisms} to improve meta-tracing efficiency. Implemented run-time optimizations, data structures, and primitives.

}}
}

%%%%%%%%%%%%%%%%%% RAX %%%%%%%%%%%%%%%%% 

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{}
{} {
\vspace{-0.4cm}
\headedsubsection % Job title entry for the current employer
{\myhref{https://github.com/cderici/rax}{Rax: A full-stack Racket to x86\_64 nanopass compiler}}
{}
{\small\bodytext{Implemented all the passes (e.g., closure conversion, register allocation, code-gen, etc.), along with garbage collection. Developed optimizations, such as inlining, loop-invariant code motion, and proper tail-calls.}}
}

%%%%%%%%%%%%%%%%%% HAZIRCEVAP %%%%%%%%%%%%%%%%% 
\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{}
{} {
\vspace{-0.4cm}
\headedsubsection % Job title entry for the current employer
{HazirCevap (Witty): A closed domain question answering system for high school students}
{}
{\small\bodytext{Government funded large scale question answering system. MSc thesis on \textsc{NLP} and Machine Learning. Led \textsc{R\&D} team (3 faculties, 4 grad students). Developed a Hidden Markov random field model for question analysis, and relevance metrics for information retrieval and response generation (see publications). Full stack in Python, and JavaScript.}}
}

\vfill \hfill \small Last compiled on \today

\newpage

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SELECTED PUBLICATIONS
%----------------------------------------------------------------------------------------

\roottitle{Selected Publications} % Top level section

\begin{itemize}
\item Flatt M., Derici C. Dybvig R. K., Keep A. et. al. “Rebuilding racket on chez scheme (experience report)”, ICFP'19

\item Derici C. et. al. “A closed-domain question answering framework using reliable resources to assist students” \newline Natural Language Engineering'18

\item Derici C. et. al. “Question analysis for a closed domain question answering system”, CICLING'15

\item Derici C. et. al. “Rule-based focus extraction in Turkish question answering systems”, SIU'14

\item Başar R. E., Derici C., and Şenol Ç. “World With Web: A compiler from world applications to JavaScript”. Technical Report, Scheme and Functional Programming Workshop'09
\end{itemize}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\roottitle{Awards \& Scholarships} % Top level section
\begin{itemize}
    \item Scholarship and award for a project on teaching natural languages to hearing impaired, 2014.
    \item Full Scholarship for PhD, 2015-2020
    \item Full Scholarship for MSc, 2012 
    \item Full Scholarship for BSc, 2005-2010
\end{itemize}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

\vfill \hfill \small Last compiled on \today

\end{document}